---
title: "Factors impacting hemoglobin A clearance in adults with sickle cell anemia on chronic transfusion therapy"
subtitle: 'Investigators: Alexandre Soares'
output: 
  word_document:
    toc: true
    toc_depth: 4
  html_document: 
    toc: true
    toc_depth: 4
    keep_md: true
      code_folding: "hide"    
editor_options: 
  chunk_output_type: console
---

Every analysis above were execute using the language `r R.version$version.string` and o software IDE (Integrated Development Environment) RStudio. Also the reports in format PDF was development for library `rmarkdown`.

Welinton Yoshio Hirai^[wyhirai@gmail.com]

```{r setup, include=F}
#clear environment
rm(list=ls(all=T))

#configurações iniciais para os chunks
knitr::opts_chunk$set(
  fig.width = 12, fig.height = 8,
  res = 300, fig.retina = 1,
  fig.align = 'center', fig.pos = 'H',
  echo = F, cache = F, warning = F, 
  message = F, packages = F,
  dev = c('png', 'pdf')
)

setwd("D:/Github/UNC_Hemoglobin")

source(file = '0_header.R')
```

# Análise 4 - Novo grupos para a variável de SCD Genotype

O paciente 52 era o único que tinha gene: _S/beta zero thalassemia_

```{r}
data1_filter %>% 
  dplyr::count(SCD_genotype_2CAT, scd_genotype_32) %>% 
  flextable::flextable() %>% 
  flextable::theme_vanilla()
```



### Stratified Yes-RBC antibodies vs. No-RBC antibodies

```{r}
data1_filter %>% 
  dplyr::select(rbc_antibodies, age_years_2, height_cm_5,
                weight_kg_6) %>% 
  # dplyr::group_by(rbc_antibodies) %>% 
  gtsummary::tbl_summary(
    by = rbc_antibodies,
    label = list(
      age_years_2 ~ 'Age',
      height_cm_5 ~ 'Height (cm)',
      weight_kg_6 ~ 'Weight (kg)'
    ),
    type = where(is.numeric) ~ 'continuous2',
    statistic = list(all_continuous() ~ c('{mean} ({sd})',
                                          '{median}',
                                          '{min} - {max}',
                                          '{p25} - {p75}'))
  ) %>% 
  gtsummary::add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% 
  gtsummary::modify_header(label = "**RBC antibodies**") %>% 
  gtsummary::bold_labels() %>% 
  gtsummary::as_flex_table() %>%
  flextable::theme_vanilla()
```
