---
title: "Factors impacting hemoglobin A clearance in adults with sickle cell anemia on chronic transfusion therapy"
subtitle: 'Investigators: Alexandre Soares'
output: 
  word_document:
    toc: true
    toc_depth: 4
  html_document: 
    toc: true
    toc_depth: 4
    keep_md: true
      code_folding: "hide"    
editor_options: 
  chunk_output_type: console
---

Every analysis above were execute using the language `r R.version$version.string` and o software IDE (Integrated Development Environment) RStudio. Also the reports in format PDF was development for library `rmarkdown`.

Welinton Yoshio Hirai^[wyhirai@gmail.com]

```{r setup, include=F}
#clear environment
rm(list=ls(all=T))

#configurações iniciais para os chunks
knitr::opts_chunk$set(
  fig.width = 12, fig.height = 8,
  res = 300, fig.retina = 1,
  fig.align = 'center', fig.pos = 'H',
  echo = F, cache = F, warning = F, 
  message = F, packages = F,
  dev = c('png', 'pdf')
)

setwd("D:/Github/UNC_Hemoglobin")

source(file = '0_header.R')
```

# Análise 4 - Novo grupos para a variável de SCD Genotype

O paciente 52 era o único que tinha gene: _S/beta zero thalassemia_

```{r}
data1_filter %>% 
  dplyr::count(SCD_genotype_2CAT, scd_genotype_32) %>% 
  flextable::flextable() %>% 
  flextable::theme_vanilla()
```

- Identificar número total de pacientes e de procedimentos realizados.

Número total de pacientes $n_{Patient} = 65$

```{r}
# length(unique(data1$patient_1))
data2 %>% 
  dplyr::count(patient_id) %>% 
  dplyr::select(!patient_id) %>% 
  gtsummary::tbl_summary(
    label = list(n ~ 'n de procedimentos realizados'),
    type = where(is.numeric) ~ 'continuous2',
    statistic = where(is.numeric) ~ c('{mean} ({sd})',
                                      '{min} | {median} | {max}')
  ) %>% 
  gtsummary::bold_labels() %>% 
  gtsummary::as_flex_table() %>%
  flextable::theme_vanilla() 
```





















